Study of the effects of magnetic braking on the lithium abundances of the Sun and solar-type stars II

### 2023-04-25 project/overleaf/paper2/mblithium.tex

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{nccmath}
\usepackage{isotope}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage[normalem]{ulem}
%\usepackage[firstpage]{draftwatermark}
%\SetWatermarkText{DRAFT}

@@

\section{Data} \label{sec_method}
The datasets provided by the Gaia mission in GEDR3 and GDR3, as well as those published by GES in DR5.0 form the main references used in this work. In general, we focus on the observations made on OCs, and particularly on those analysed in the \cite{Bragaglia2022} and \cite{Randich2022} papers. On the basis of the results presented in these papers, a set of 65 OCs are selected as the reference dataset for our work.

\begin{table}
	\centering
	\caption{Information on the pre-selected OCs.}
	\label{tab:oc_list}
	\begin{tabular}{l l l l} 
		\hline
		Cluster & GES\_FLD & age (Gyr) & [Fe/H]\\
		\hline
            25 Ori & 25\_Ori & 0.013 & 0 \\
            ASCC 50 & Assc50 & 0.011 & 0.02 \\
            Berkeley 21 & Br21 & 2.138 & -0.21 \\
            Berkeley 22 & Br22 & 2.455 & -0.26 \\
            Berkeley 25 & Br25 & 2.455 & -0.25 \\
            Berkeley 30 & Br30 & 0.295 & -0.13 \\
            Berkeley 31 & Br31 & 2.818 & -0.29 \\
            Berkeley 32 & Br32 & 4.898 & -0.31 \\
            Berkeley 36 & Br36 & 6.761 & -0.15 \\
            Berkeley 39 & Br39 & 5.623 & -0.14 \\
            Berkeley 44 & Br44 & 1.445 & 0.22 \\
            Berkeley 73 & Br73 & 1.413 & -0.26 \\
            Berkeley 75 & Br75 & 1.738 & -0.34 \\
            Berkeley 81 & Br81 & 1.148 & 0.22 \\
            Blanco 1 & Blanco1 & 0.105 & -0.03 \\
            Chamaeleon I & Cha\_I & 0.001 & -0.03 \\
            Collinder 197 & Col197 & 0.014 & 0.03 \\
            Collinder 69 & lam\_Ori & 0.013 & -0.09 \\
            Czernik 24 & Cz24 & 2.692 & -0.11 \\
            Czernik 30 & Cz30 & 2.884 & -0.31 \\
            ESO 92-05 & ESO92\_05 & 4.467 & -0.29 \\
            Haffner 10 & Haf10 & 3.802 & -0.1 \\
            IC 2391 & IC2391 & 0.029 & -0.06 \\
            IC 2602 & IC2602 & 0.036 & -0.06 \\
            IC 4665 & IC4665 & 0.033 & 0.01 \\
            Loden 165 & Loden165 & 3 &  \\
            Messier 67 & M67 & 3.981 & -0.02 \\
            NGC 2141 & NGC2141 & 1.862 & -0.04 \\
            NGC 2158 & NGC2158 & 1.549 & -0.15 \\
            NGC 2232 & NGC2232 & 0.018 & -0.03 \\
            NGC 2243 & NGC2243 & 4.365 & -0.45 \\
            NGC 2244 & NGC2244 & 0.004 & -0.04 \\
            NGC 2264 & NGC2264 & 0.003 & -0.1 \\
            NGC 2355 & NGC2355 & 1 & -0.13 \\
            NGC 2420 & NGC2420 & 1.698 & -0.15 \\
            NGC 2425 & NGC2425 & 2.399 & -0.13 \\
            NGC 2451A & NGC2451 & 0.035 & -0.08 \\
            NGC 2451B & NGC2451 & 0.041 & -0.02 \\
            NGC 2516 & NGC2516 & 0.24 & -0.04 \\
            NGC 2547 & NGC2457 & 0.032 & -0.03 \\
            NGC 3293 & NGC3293 & 0.01 & -0.08 \\
            NGC 3532 & NGC3532 & 0.398 & -0.01 \\
            NGC 3766 & NGC3766 & 0.023 & -0.12 \\
            NGC 4815 & NGC4815 & 0.372 & 0.08 \\
            NGC 6005 & NGC6005 & 1.259 & 0.22 \\
            NGC 6067 & NGC6067 & 0.126 & 0.03 \\
            NGC 6253 & NGC6253 & 3.246 & 0.33 \\
            NGC 6259 & NGC6259 & 0.269 & 0.18 \\
            NGC 6281 & NGC6281 & 0.513 & -0.04 \\
            NGC 6405 & NGC6405 & 0.035 & -0.02 \\
            NGC 6530 & NGC6530 & 0.002 & -0.02 \\
            NGC 6633 & NGC6633 & 0.692 & -0.03 \\
            NGC 6649 & NGC6649 & 0.071 & -0.08 \\
            NGC 6705 & NGC6705 & 0.309 & 0.03 \\
            NGC 6709 & NGC6709 & 0.191 & -0.02 \\
            NGC 6802 & NGC6802 & 0.661 & 0.14 \\
            Pismis 15 & Pismis15 & 0.871 & 0.02 \\
            Pismis 18 & Pismis18 & 0.575 & 0.14 \\
            Ruprecht 134 & Rup134 & 1.66 & 0.27 \\
            Trumpler 14 & Trumpler14 & 0.003 & -0.01 \\
            Trumpler 20 & Trumpler20 & 1.862 & 0.13 \\
            Trumpler 23 & Trumpler23 & 0.708 & 0.2 \\
            Trumpler 5 & Trumpler5 & 4.266 & -0.35 \\
            Gamma Vel & gamma2\_vel & 0.02 & -0.02 \\
            Rho Oph & Rho\_Oph & 0.001 & 0.03 \\
		\hline
	\end{tabular}
\end{table}

@@

@@

\cite{Cranmer2011} found that the magnetic field strength is mainly influenced by $f_*$ rather than by the rotation period of the star. That is, variations in the star's angular velocity do not significantly alter its magnetic field strength. In addition, $f_*$ has a strong dependence on the Rossby number ($\rossby$). In order to calculate $\rossby$ of a given star, it is necessary to know the turn over time ($\turnover$),
\begin{ceqn}
\begin{equation}
    \rossby = \frac{\prot}{\turnover} \label{eq:mf_rossby}
\end{equation}
\begin{ceqn}
\begin{equation}
    \turnover = 314.24\;exp\left[-\Bigg(\frac{\teff}{1952.5}\Bigg)-\Bigg(\frac{\teff}{6250}\Bigg)^{18} \;\right]+0.002 \label{eq:mf_turnover}
\end{equation}

\end{ceqn}
\cite{Cranmer2011} Crammer provides two different settings for $f_*$ which define respectively the upper and lower limits for the mean surface magnetic field strength ($f_*B_*$),

@@

\begin{figure}
	\includegraphics[trim = 10mm 10mm 15mm 10mm, clip,width=\columnwidth]{figures/hr_var_vel_0_0g_z1.eps}
    \caption{An example solar 1$\msun$ grid of stellar evolutionary track from PMS till TAMS covering a wide range of angular velocities. The rotation is activated in the models in the PMS and those models reach before the ZAMS and at a lower $\teff$ than the non-rotating one (solid black line). The luminosity is expressed in terms of $\lsun$.}
    \label{fig:hr_var_vel_0g}
\end{figure}

@@

\appendix

\section{Mesh models visualization}
The following figures comprise a series of grids as a function of time and for several 1 $\msun$ models in which on the one hand, the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H} for both variable magnetic field intensities and angular velocities and on the other hand, the evolution of surface rotational velocity are shown.

@@

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{nccmath}
\usepackage{isotope}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage[normalem]{ulem}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{longtable}
%\usepackage[firstpage]{draftwatermark}
%\SetWatermarkText{DRAFT}

@@

\section{Data} \label{sec_method}
The datasets provided by the Gaia mission in GEDR3 and GDR3, as well as those published by GES in DR5.0 form the main references used in this work. In general, we focus on the observations made on OCs, and particularly on those analysed in the \cite{Bragaglia2022} and \cite{Randich2022} papers. On the basis of the results presented in these papers, a set of 65 OCs (see Table \ref{tab:oc_list}) are selected as the reference dataset for our work.

\begin{table*}
	\centering
	\begin{tabular}{|l l l l l || c c c c c | c c c c c|} 
		\hline
             & & & & & & & $\oomegac$ & & & & & $\oomegac$ & & \\
		Open Cluster & GES\_FLD & Age (Gyr) & [Fe/H] & $N_*$ & 0.095 & 0.10 & 0.105 & 0.11 & 0.115 & 0.12 & 0.125 & 0.13 & 0.14 & 0.1425\\
		\hline
            25 Ori & 25\_Ori & 0.013 & 0 & 294 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            ASCC 50 & Assc50 & 0.011 & 0.02 & 1225 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            Berkeley 21 & Br21 & 2.138 & -0.21 & 744 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 1\\
            Berkeley 22 & Br22 & 2.455 & -0.26 & 395 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 25 & Br25 & 2.455 & -0.25 & 81 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 30 & Br30 & 0.295 & -0.13 & 332 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 31 & Br31 & 2.818 & -0.29 & 616 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 32 & Br32 & 4.898 & -0.31 & 438 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 36 & Br36 & 6.761 & -0.15 & 739 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            Berkeley 39 & Br39 & 5.623 & -0.14 & 899 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 2 & 2\\
            Berkeley 44 & Br44 & 1.445 & 0.22 & 93 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 73 & Br73 & 1.413 & -0.26 & 77 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 75 & Br75 & 1.738 & -0.34 & 75 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Berkeley 81 & Br81 & 1.148 & 0.22 & 279 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Blanco 1 & Blanco1 & 0.105 & -0.03 & 463 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Chamaeleon I & Cha\_I & 0.001 & -0.03 & 709 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Collinder 197 & Col197 & 0.014 & 0.03 & 409 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Collinder 69 & lam\_Ori & 0.013 & -0.09 & 836 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Czernik 24 & Cz24 & 2.692 & -0.11 & 346 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Czernik 30 & Cz30 & 2.884 & -0.31 & 226 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            ESO 92-05 & ESO92\_05 & 4.467 & -0.29 & 212 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Haffner 10 & Haf10 & 3.802 & -0.1 & 562 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            IC 2391 & IC2391 & 0.029 & -0.06 & 434 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            IC 2602 & IC2602 & 0.036 & -0.06 & 1836 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0\\
            \rowcolor{lightgray}
            IC 4665 & IC4665 & 0.033 & 0.01 & 567 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0\\
            Loden 165 & Loden165 & 3 &  & 388 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            Messier 67 & M67 & 3.981 & -0.02 & 131 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6\\
            \rowcolor{lightgray}
            NGC 2141 & NGC2141 & 1.862 & -0.04 & 853 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1\\
            NGC 2158 & NGC2158 & 1.549 & -0.15 & 616 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 2232 & NGC2232 & 0.018 & -0.03 & 1866 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 2243 & NGC2243 & 4.365 & -0.45 & 661 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 2244 & NGC2244 & 0.004 & -0.04 & 452 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 2264 & NGC2264 & 0.003 & -0.1 & 1857 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            NGC 2355 & NGC2355 & 1 & -0.13 & 208 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1\\
            \rowcolor{lightgray}
            NGC 2420 & NGC2420 & 1.698 & -0.15 & 562 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1\\
            \rowcolor{lightgray}
            NGC 2425 & NGC2425 & 2.399 & -0.13 & 528 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1\\
            \rowcolor{lightgray}
            NGC 2451 & NGC2451 & 0.035 & -0.08 & 1656 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 1\\
            \rowcolor{lightgray}
            NGC 2516 & NGC2516 & 0.24 & -0.04 & 759 & 0 & 0 & 0 & 1 & 1 & 1 & 3 & 4 & 4 & 3\\
            NGC 2547 & NGC2457 & 0.032 & -0.03 & 477 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 3293 & NGC3293 & 0.01 & -0.08 & 584 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            NGC 3532 & NGC3532 & 0.398 & -0.01 & 1145 & 1 & 1 & 0 & 1 & 1 & 1 & 1 & 1 & 0 & 1\\
            NGC 3766 & NGC3766 & 0.023 & -0.12 & 399 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 4815 & NGC4815 & 0.372 & 0.08 & 218 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            NGC 6005 & NGC6005 & 1.259 & 0.22 & 560 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 1\\
            NGC 6067 & NGC6067 & 0.126 & 0.03 & 780 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 6253 & NGC6253 & 3.246 & 0.33 & 646 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            NGC 6259 & NGC6259 & 0.269 & 0.18 & 494 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
            \rowcolor{lightgray}
            NGC 6281 & NGC6281 & 0.513 & -0.04 & 320 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1\\
            \rowcolor{lightgray}
            NGC 6405 & NGC6405 & 0.035 & -0.02 & 701 & 1 & 1 & 1 & 0 & 1 & 3 & 2 & 0 & 0 & 0\\
            NGC 6530 & NGC6530 & 0.002 & -0.02 & 1983 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            NGC 6633 & NGC6633 & 0.692 & -0.03 & 1662 & 2 & 2 & 2 & 1 & 1 & 0 & 0 & 0 & 1 & 1\\
            NGC 6649 & NGC6649 & 0.071 & -0.08 & 283 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            NGC 6705 & NGC6705 & 0.309 & 0.03 & 1066 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            NGC 6709 & NGC6709 & 0.191 & -0.02 & 730 & 2 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1\\
            NGC 6802 & NGC6802 & 0.661 & 0.14 & 197 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Pismis 15 & Pismis15 & 0.871 & 0.02 & 333 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Pismis 18 & Pismis18 & 0.575 & 0.14 & 142 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Ruprecht 134 & Rup134 & 1.66 & 0.27 & 680 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Trumpler 14 & Trumpler14 & 0.003 & -0.01 & 1902 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            \rowcolor{lightgray}
            Trumpler 20 & Trumpler20 & 1.862 & 0.13 & 1213 & 3 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 2\\
            Trumpler 23 & Trumpler23 & 0.708 & 0.2 & 165 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Trumpler 5 & Trumpler5 & 4.266 & -0.35 & 1138 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Gamma Vel & gamma2\_vel & 0.02 & -0.02 & 1269 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
            Rho Oph & Rho\_Oph & 0.001 & 0.03 & 311 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\           
            \hline
	\end{tabular}
 	\caption{List of selected OCs. For each OC, name, GES denomination, estimated age, metallicity and number of components are listed. The number of OC components selected by the different simulations are shown separately. This information is split into two groups, each corresponding to the set of simulations used in the figures shown in the following sections. Finally, those OCs that have been selected in any of the simulations are highlighted in grey.}
  	\label{tab:oc_list}
\end{table*}

\begin{table*}
	\centering
	\begin{tabular}{l l l l l l l} 
		\hline
            ObjectId & $\teff$(K) & $\gsurf$(dex) & FeH(dex) & ALi(dex) & eALi(dex) & Age(Gyr)\\
		\hline
            8510914\_1157003 & 5843 & 4.42 & -0.03 & 1.8 & 0.08 & 3.981\\ 
            8510991\_1146169 & 5797 & 4.4 & -0.01 & 1.65 & 0.08 & 3.981\\ 
            8512177\_1144050 & 5818 & 4.46 & 0 & 1.99 & 0.06 & 3.981\\ 
            8513941\_1200571 & 5792 & 4.41 & -0.02 & 1.49 & 0.13 & 3.981\\ 
            8515559\_1148381 & 5794 & 4.43 & -0.04 & 1.56 & 0.1 & 3.981\\ 
            8520350\_1147480 & 5875 & 4.47 & -0.03 & 1.21 & 0.24 & 3.981\\ 
            \hline
	\end{tabular}
 	\caption{M64 - Filter setup: $\teff$ low=5789.184, $\teff$ top=5889.6435, $\gsurf$ low=4.3945, $\gsurf$ top=4.4939, $\feh$ low=-0.05, $\feh$ top=0.05, Age low=3.977, Age top=3.985}
	\label{tab:oc_m64}
\end{table*}

\begin{table*}
	\centering
	\begin{tabular}{l l l l l l l} 
		\hline
            ObjectId & $\teff$(K) & $\gsurf$(dex) & FeH(dex) & ALi(dex) & eALi(dex) & Age(Gyr)\\
		\hline
            12392824-6041134 & 5831 & 4.54 & 0.01 & 2.66 & 0.08 & 1.862\\ 
            12401318-6037507 & 5810 & 4.54 & 0 & 2.35 & 0.12 & 1.862\\ 
            12402039-6042428 & 5824 & 4.48 & 0.02 & 2.05 & 0 & 1.862\\ 
            \hline
	\end{tabular}
 	\caption{Trumpler20 - Filter setup: $\teff$ low=5731.2886, $\teff$ top=5831.2886, $\gsurf$ low=4.4518, $\gsurf$ top=4.5518, $\feh$ low=-0.05, $\feh$ top=0.05, Age low=1.8601, Age top=1.8639}
	\label{tab:oc_trumpler20}

\end{table*}

@@

Tables \ref{tab:oc_m64} and \ref{tab:oc_trumpler20} show the subset of components of OC M67 and Trumpler 20 selected during the simulations for models initialised with $\oomegac$ = 0.14. Each of the tables lists the GES identifier of the star and the $\teff$, $\gsurf$, $\feh$, A(Li) and estimated age ranges used in the simulation.

@@

\cite{Cranmer2011} found that the magnetic field strength is mainly influenced by $f_*$ rather than by the rotation period of the star. That is, variations in the star's angular velocity do not significantly alter its magnetic field strength. In addition, $f_*$ has a strong dependence on the Rossby number ($\rossby$). In order to calculate $\rossby$ of a given star, it is necessary to know the turn over time ($\turnover$),
\begin{ceqn}
\begin{equation}
    \rossby = \frac{\prot}{\turnover} \label{eq:mf_rossby}
\end{equation}
\begin{equation}
    \turnover = 314.24\;exp\left[-\Bigg(\frac{\teff}{1952.5}\Bigg)-\Bigg(\frac{\teff}{6250}\Bigg)^{18} \;\right]+0.002 \label{eq:mf_turnover}
\end{equation}
\end{ceqn}
\cite{Cranmer2011} Crammer provides two different settings for $f_*$ which define respectively the upper and lower limits for the mean surface magnetic field strength ($f_*B_*$),

@@

\begin{figure}
	\includegraphics[trim = 10mm 10mm 15mm 10mm, clip,width=\columnwidth]{figures/paper1/hr_var_vel_0_0g_z1.eps}
    \caption{An example solar 1$\msun$ grid of stellar evolutionary track from PMS till TAMS covering a wide range of angular velocities. The rotation is activated in the models in the PMS and those models reach before the ZAMS and at a lower $\teff$ than the non-rotating one (solid black line). The luminosity is expressed in terms of $\lsun$.}
    \label{fig:hr_var_vel_0g}
\end{figure}

@@

\appendix
\clearpage
\section{Mesh models visualization}
The following figures comprise a series of grids as a function of time and for several 1 $\msun$ models in which on the one hand, the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H} for both variable magnetic field intensities and angular velocities and on the other hand, the evolution of surface rotational velocity are shown.

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
